---
title: "Data-Processing"
author: "Yasin Kaymaz"
date: "1/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("https://raw.githubusercontent.com/yasinkaymaz/cellRtools/master/main/functions.R")
```


# Tasic 2018 dataset
## Optain the ALM dataset from Allen Inst.

```{bash}
#wget http://celltypes.brain-map.org/api/v2/well_known_file_download/694413179
#unzip mouse_ALM_gene_expression_matrices_2018-06-14.zip
```

After downloading the data, unzip the file and use the exon based gene **count** matrix for further analysis.

For the processing details, please follow code/WP_codes.R

```{r echo=FALSE}

load("data/Tasic2018-reAnalysis.RData")
```

## TSNE plots of All ALM cells in the study 

### Colored by brain subregions
```{r echo=FALSE}
TSNEPlot(Tasic2018, group.by="brain_subregion")
```

### Colored by brain subclasses
```{r echo=FALSE}
TSNEPlot(Tasic2018, group.by="subclass")
```

### Colored by brain cell types
```{r echo=FALSE}
TSNEPlot(Tasic2018, group.by="class")
```

## Only cell clusters of interest

    "L5 IT ALM Cbln4 Fezf2",
    "L5 IT ALM Cpa6 Gpr88",
    "L5 IT ALM Gkn1 Pcdh19",
    "L5 IT ALM Lypd1 Gpr88",
    "L5 IT ALM Pld5",
    "L5 IT ALM Tmem163 Arhgap25",
    "L5 IT ALM Tmem163 Dmrtb1",
    "L5 IT ALM Tnc",
    "L5 PT ALM Hpgd",
    "L5 PT ALM Npsr1",
    "L5 PT ALM Slco2a1"

```{r echo=FALSE}

TSNEPlot(L5ALM.ITPT, group.by="brain_subregion")
TSNEPlot(L5ALM.ITPT, group.by="subclass")
TSNEPlot(L5ALM.ITPT, group.by="class")
TSNEPlot(L5ALM.ITPT, group.by="cluster", do.label = T)
TSNEPlot(L5ALM.ITPT, group.by="res.1", do.label = T)

```
