---
title: "DE_L5_IT-PT"
author: "Yasin Kaymaz"
date: "1/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(DT)
library(tidyverse)
options(width = 80)
source("https://raw.githubusercontent.com/yasinkaymaz/cellRtools/master/main/functions.R")
```

# Differentially expressed genes between PT and IT

```{r echo=FALSE}
load("~/data/Tasic2018-reAnalysis_L5ITPT.RData")
```

Comparing all IT cells to PT cells within the L5 layer using MAST test.

```{r echo=FALSE, message=FALSE, warning=FALSE}
volcanoPlotly(allmarkers.subclass)
```

### Table for genes with significantly higher expression in **IT**:

(padj < 0.01, avglogFC > 0.2)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
allmarkers.subclass  %>% 
  select(-p_val)%>% 
  filter(cluster == "L5 IT") %>% 
  filter(p_val_adj < 0.01) %>%
  filter(avg_logFC > 0.2) %>%
  filter(pct.1 > 0.5) %>% filter( ((pct.1 - pct.2)/max(pct.1,pct.2) > 0.7)) %>%
  datatable( extensions = 'Scroller', options = list(
    deferRender = TRUE,
    scrollY = 200,
    scroller = TRUE
  ))
```


### Table for genes with significantly higher expression in **PT**:

(padj < 0.01, avglogFC > 0.2)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
allmarkers.subclass  %>% 
  select(-p_val) %>% 
  filter(cluster == "L5 PT") %>% 
  filter(p_val_adj < 0.01) %>%
  filter(avg_logFC > 0.2) %>%
  filter(pct.1 > 0.5) %>% filter( ((pct.1 - pct.2)/max(pct.1,pct.2) > 0.7)) %>%
  datatable( extensions = 'Scroller', options = list(
    deferRender = TRUE,
    scrollY = 200,
    scroller = TRUE
  ))
```

## Expression heatmap of top 200 differentially expressed genes between **IT and PT**

```{r echo=FALSE, message=F, warning=F, fig.height=20, fig.width=20}
top100 <- allmarkers.subclass %>% filter(p_val_adj < 0.01) %>% filter(pct.1 > 0.5) %>% filter( ((pct.1 - pct.2)/max(pct.1,pct.2) > 0.7)) %>% group_by(cluster) %>% top_n(100, avg_logFC)
L5ALM.ITPT = SetAllIdent(L5ALM.ITPT, id = 'subclass')
DoHeatmap(object = L5ALM.ITPT, genes.use = top100$gene, slim.col.label = TRUE, remove.key = TRUE,group.label.loc="top",group.label.rot=T)
```

## Same heatmap as above except cells are grouped into subcategories

```{r echo=FALSE, message=F, warning=F, fig.height=20, fig.width=20}
top20 <- allmarkers.cluster %>% filter(p_val_adj < 0.01) %>% group_by(cluster) %>% top_n(20, avg_logFC)
L5ALM.ITPT = SetAllIdent(L5ALM.ITPT, id = 'cluster')
DoHeatmap(object = L5ALM.ITPT, genes.use = top20$gene, slim.col.label = TRUE, remove.key = TRUE,group.label.loc="top",group.label.rot=T)
```




.

.

.

.

.

.
