---
title: "IT-PT_Contrasts"
author: "Yasin Kaymaz"
date: "1/31/2019"
output:
  html_document:
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(DT)
library(tidyverse)
source("https://raw.githubusercontent.com/yasinkaymaz/cellRtools/master/main/functions.R")
source("code/functions.R")

load("~/data/markers.L5IT.vs.Gaba.Rdata")
load("~/data/markers.L5IT.vs.Glu.Rdata")
load("~/data/markers.L5IT.vs.Gaba_Glu.Rdata")
load("~/data/markers.L5PT.vs.Gaba.Rdata")
load("~/data/markers.L5PT.vs.Glu.Rdata")
load("~/data/markers.L5PT.vs.Gaba_Glu.Rdata")

```

# L5 IT cell contrasts:

## IT cells - Contrast against Glutamatergic neurons

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Glu)))
InteractiveTable(FilterTable(markers.L5IT.vs.Glu))
```


## IT cells - Contrast against GABAergic neurons

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Gaba)))
InteractiveTable(FilterTable(markers.L5IT.vs.Gaba))
```

## IT cells - Contrast against both Glutamatergic and GABAergic neurons

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Gaba_Glu)))
InteractiveTable(FilterTable(markers.L5IT.vs.Gaba_Glu))
```


# L5 PT cell contrasts:

## PT cells - Contrast against Glutamatergic neurons

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5PT.vs.Glu)))
InteractiveTable(FilterTable(markers.L5PT.vs.Glu))
```


## PT cells - Contrast against GABAergic neurons

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5PT.vs.Gaba)))
InteractiveTable(FilterTable(markers.L5PT.vs.Gaba))
```

## PT cells - Contrast against both Glutamatergic and GABAergic neurons

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5PT.vs.Gaba_Glu)))
InteractiveTable(FilterTable(markers.L5PT.vs.Gaba_Glu))
```



.

.

.

.

.

.

